Tropical Andes plant traits

### 2023-10-04 archive/L2_1_TropicalAndes_plant_traits.Rmd
clean repo - update names and move old code to archive

# Write data to csv
```{r}
write.csv(plant_traits, file.path(output_path,"TropicalAndes_plant_traits_forest.csv"))
write.csv(species_list, file.path(output_path,"TropicalAndes_plant_traits_forest_species_list.csv"))
```

>>>>

```{r}
plant_traits_wide_complete$dispersal_syndrome <- as.character(plant_traits_wide_complete$dispersal_syndrome)
plant_traits_wide_complete$plant_lifespan <- as.character(plant_traits_wide_complete$plant_lifespan)
```

# Write data to csv
```{r}
write.csv(plant_traits_wide_complete, file.path(output_path,"TropicalAndes_plant_traits_forest.csv"))
write.csv(species_list, file.path(output_path,"TropicalAndes_plant_traits_forest_species_list.csv"))
```
